Scientific Reasoning with LLMs

### 2024-10-28 docs/proposal/main.tex
rewrite paragraph on knowledge distillation

Knowledge distillation allows to obtain smaller models capable of successfully following the behavior of larger "teacher" models. This is particularly useful for privacy reasons (running AI applications on mobile devices) and for cases where access to very large models in the cloud is not guaranteed (e.g. in cars). Some approaches to knowledge distillation include: \begin{itemize}
    \item distillation of outputs
    \item distillation of features on intermediate layers 
    \item CoT knowledge distillation \cite{shridhar2022distilling} 
    \item \katja{it's a draft TODO: add info from Dasha's slides}
\end{itemize}
Our goal is to test whether any of these techniques can be successfully used to obtain a model with scientific reasoning capabilities.

>>>>

\paragraph{Knowledge distillation (KD)} allows to obtain smaller models capable of successfully following the behavior of larger teacher models. This is particularly useful for privacy reasons (running AI applications on mobile devices) and for cases where access to very large models in the cloud is not guaranteed (e.g. in cars). The teacher model can be used to intelligently select examples on which the student model is trained (dataset distillation) \cite{yu2023dataset}, while \cite{li2024turning} rely on negative samples to show the student what incorrect answers or reasoning paths it should avoid to improve task accuracy. Training small models on a CoT reasoning path of a larger model was also shown to be a way to obtain a small student model replicating reasoning capabilities of teacher on downstream tasks \cite{magister2022teaching}, which is close to _response-based KD_ where the student model mimics the output of the teacher. More effective can be _feature-based KD_ where student also partially replicates the teacher on a feature-based level, when knowledge from specific layers of the teacher model is distilled into the student model \cite{sepahvand2022teacher}, while the student model's structure may be a quantized, simplified, or condensed version of the teacher's architecture \cite{gou2021knowledge}.

\katja{Crazy idea: can we distill a reasoning path of a whole agent into a smaller model? I.e. instead of intelligent decision making that a large model performs for a complex task (search for X first, then look up Y, then formulate hypotheses Z) the student model learns the "protocols" of "customer support" and acts accordingly, without actually "understanding" why a particular action is good in a particular situation}
